\externaldocument{chap_03}
\chapter{Theory and Key Concepts}

\section*{Introduction}

\section{What is Debugging?}
During the development process of a project, specifically within computer programs, mistakes are bound to happen and it is unlikely that the first iteration of a solution will be flawless, and therefore, defects exist within the application. Debugging is the process of finding and eliminating these defects. But what defines a defect or the fact that a program is not working properly?

When writing a program, we have a goal in mind that we want to achieve, let's call this the \textit{specification}, for example, we would like to create a program that blinks an LED at a periodic rate, if say the LED is not toggling, or the timing is not consistent, we can confidently say that the program is not working according to the specification, and therefore, within the context of our work, it contains a bug. The next step is then to fix our program, and that process is exactly what's called debugging.

A specification generally sets a final result or an end goal, but it also implicitly implies how parts of the system should behave in order to achieve that. For example, the end goal is a periodically blinking LED, but that implies that we should be supplying current to the LED at a specific rate, and since we're using a microcontroller, that in itself implies that we should be writing values to specific registers in order to achieve that functionality. If any of these break, then the symptom would appear as the LED not blinking properly, due to writing to the wrong register for example.

The coupling between "bugs" and specifications is important and should be highlighted clearly, as the same program could be considered buggy under certain specifications while it works perfectly fine in other cases, and that leads us to the last part: defining an erroneous state.

\subsection{What is an erroneous state?}
We established that a lot can go wrong during the development of a program, and to figure out what's wrong, we need to define how the functional state of the program should look like.
We can go about the definition by first making the distinction from other faulty behaviors that can occur. The most notable one is error handling within the program, as we know certain operations might fail in advance for whatever reason, we account for this by checking for the status of the operation after its completion, we then have the possibility of altering the control flow based on the status of the operation, or potentially halting the execution entirely.

Error handling can be part of the specification, and is not the subject of discussion, instead, an erroneous state is one that can potentially lead to an unexpected execution flow, or result in undesired behavior without being accounted for. This can be due to the assumption that a program cannot reach such a state, or that the program in itself simply does something that contradicts the specification. As an example, consider a program that takes as an input an integer number, and executes a specific piece of code only if that number is even.
\begin{lstlisting}[language=C, caption=Checking Parity]
void foo(int x){
    if(x % 2 == 0) {
        //Do some treatment...
    }
}
\end{lstlisting}
By mistakenly changing the checking condition to:
\begin{lstlisting}[language=C, caption=Checking Parity]
if(x % 2 != 0)
\end{lstlisting}
We are now doing the processing on odd values of our variable, while this will not necessarily crash our program, it differs from what is defined in the specification, and therefore will lead to unexpected consequences. And, relatively to the processing block inside the conditional statement, the erroneous state in this case is the parity of our integer.

This small example showcases the complexity of the problem, as we cannot assume that our program is working properly according to the specifications, and we have to figure out how to analyze our program to find out that the root cause of the erroneous state is the wrong conditional check we apply.
However, by checking the value of the variable during runtime, we can remark that it only enters the processing block when it is odd, and we can infer that the control flow is not propagating properly based on the parity, which can allow us to limit our analysis to statements that influence the state (parity) of the variable, which in our case is simply the conditional check. Marking elements and operations that make assumptions about the state, such as control flow will allow us to limit the scope of our analysis, and thus improve the quality of the debugging workflow.
\section{Embedded Systems Debugging}
