\chapter*{Conclusion}
\addcontentsline{toc}{chapter}{Conclusion}
\markboth{Conclusion}{}

This summer internship project at STMicroelectronics Tunis has been a comprehensive journey into embedded systems development, focusing on automating the execution of the CoreMark benchmark on STM32 microcontrollers using the Csolution project structure. Beginning with an exploration of the internship context, including ST's global presence and support solutions, the project addressed the challenges of manual benchmarking processes, critiqued existing approaches, and proposed an innovative automated solution.
The theoretical foundations laid in Chapter 2 provided essential knowledge on STM32 MCUs, benchmarking principles, build processes, debugging techniques, and the Open-CMSIS-Pack ecosystem. This groundwork informed the specification of functional and non-functional requirements, structural decisions for the CoreMark project and generation tool, and the selection of hardware and software resources, as detailed in Chapter 3.
The core of the project, presented in Chapter 4, involved porting CoreMark to STM32 devices, integrating it with Csolution, defining a modular project architecture, and developing the \texttt{cm\_gen} CLI tool for fully automated project generation. By identifying automatable patterns and leveraging templates, metadata, and dynamic configurations, \texttt{cm\_gen} ensures seamless compatibility across all STM32 families and compilers. Validation through extensive testing established a reliable baseline for performance metrics, confirming the solution's robustness.
Overall, this project has successfully streamlined benchmarking workflows, reducing manual effort and enhancing efficiency for embedded developers. It demonstrates the power of automation in addressing real-world engineering challenges and positions the developed tools for future extensions, such as support for emerging STM32 devices or additional benchmarks.
On a personal level, this internship has enriched my technical skills in embedded programming, tool development, and project management, while fostering a deeper appreciation for collaborative innovation in a professional setting. I am grateful for the opportunity and look forward to applying these insights in future endeavors.
