
%=== File containing Global Configuration of the report ===%
%                                                          %
% Copyright (C) ISI - All Rights Reserved                  %
% Proprietary                                              %
% Written by Med Hossam <med.hossam@gmail.com>, April 2016 %
%                                                          %
% @author: HEDHILI Med Houssemeddine                       %
% @linkedin: http://tn.linkedin.com/in/medhossam           %
%==========================================================%

%=========== You MUST type your information here ==========%
% global_config.tex file is designed to configure your     %
% cover pages (main, back and black covers)                %
%==========================================================%

%============= Config new columns type ==============%
\newcolumntype{L}{>{\raggedright\arraybackslash}}
\newcolumntype{R}{>{\raggedleft\arraybackslash}}
\newcolumntype{C}{>{\centering\arraybackslash}}
%==================================================%

%========= Config the cover section ==========%

\title{Trace \& Debug Features in STM32 Microcontrollers}

\author{Youssef HASNAOUI}
%%% if necessary
% Set isBinomal to true and type second author name
%\setboolean{isBinomal}{true}
%\secondAuthor{Prénom NOM}

\diplomaName{National Diploma in Infotronics Systems Engineering}
\speciality{Microelectronics \& Embedded Systems}
%\speciality{Génie des Télécommunications et Réseaux}
%\speciality{Génie Informatique des Systèmes Industriels}

%% Encadrant professionnel
\proFramerNameOne{Mohamed HAMROUNI}
\proFramerSpecialityOne{Application Engineer}

\academicFramerName{Faten Salem}
\academicFramerSpeciality{Professor}

%% Entreprise d'accueil
\companyName{STMicroelectronics}

%% Année universitaire
\collegeYear{2025 - 2026}

%%%%%% Signatures section %%%%%%

% You can simply remove theses sentences by typing an empty string
% \proSignSentence{}

\proSignSentence{J'autorise l'étudiant à faire le dépôt de son rapport de stage en vue d'une soutenance.}


%%% AR

%% To use latin characters inside the arabic text
% just put them inside the command \textLR{}
%%%%

%%% FR
\frenchAbstract{Ce rapport décrit les travaux réalisés lors de mon stage d'été chez STMicroelectronics, axé sur l'analyse comparative indépendante de la plateforme. L'objectif principal était d'exécuter Coremark sur des microcontrôleurs STM32 en utilisant la structure de projet Csolution. Pour ce faire, j'ai mis à profit mes connaissances en développement logiciel et embarqué, en compilation et génération de code C, à l'aide d'outils tels que CMSIS-Toolbox, C et Golang. Les résultats ont permis de réduire considérablement le temps nécessaire à la configuration et à l'exécution des projets Coremark avec plusieurs compilateurs, tout en optimisant les résultats. Ce stage m'a également permis de renforcer mes compétences en compilation, en conception d'architecture de projets embarqués et de mieux comprendre les défis spécifiques de l'ingénierie des systèmes embarqués.}

\frenchAbstractKeywords{C/C++, Golang, Systèmes embarqués, STM32, Compilation, Génération de Code.}

%% dont go over 10 lines
%%% EN
\englishAbstract{This report describes the work carried out during my summer internship at STMicroelectronics, focused on platform-agnostic benchmarking. The main objective was to run Coremark on STM32 devices using Csolution project structure. To achieve this, I put to use my knowledge in software and embedded development,C code compilation and code generation, using tools such as CMSIS-Toolbox, C and Golang. The results helped to drastically reduce the time required to setup and run Coremark projects using multiple compilers, as well as generating the most optimal results. This internship also allowed me to strengthen my skills in the compilation process, embedded projects architecture design and gain insight into the specific challenges of embedded systems engineering.}

\englishAbstractKeywords{C/C++, Golang, Embedded Systems, STM32, Compilation, Code Generation.}

%% if you want to get rid of the company address just set the boolean variable to false
% PS : it's optional
\setboolean{wantToTypeCompanyAddress}{false}

\companyEmail{contact@company.com}
\companyTel{71 111 111}
\companyFax{71 222 222}
\companyAddressAR{نهج بحيرة ملاران - ضفاف البحيرة - تونس}
\companyAddressFR{Rue du Lac Malaren, Les Berges du Lac 1053 Tunis}
